\begin{center}

\vspace{7cm}
\LARGE{\textbf{ACKNOWLEDGEMENT}}\\[1cm]
\end{center}
\linespread{1}

\large{\paragraph{}
I extend my sincere gratitude to all those who have played crucial roles in the successful development of the Quiz App project for the Bachelor of Technology (B.Tech.) program. This achievement would not have been possible without the unwavering support, encouragement, and expertise of various individuals and organizations.}

\large{\paragraph{}
A special acknowledgment is extended to \textbf{SKIT College} for providing the essential platform and resources that facilitated the practical application of theoretical knowledge in the development of the Quiz App. I am sincerely grateful for the guidance and mentorship of \textbf{Mr. Subham Gupta Sir}, whose insights have been invaluable throughout the development process. Their expertise has significantly enriched my understanding of the subject matter.}

\large{\paragraph{}
I express my deep appreciation to the esteemed faculty at \textbf{Swami Keshvanand Institute of Technology Management \& Gramothan}, particularly \textbf{Dr. (Prof.) Anil Chaudhary}, Head of the Department of Information Technology, for their continuous guidance and mentorship. Dr. Chaudhary's leadership has played a pivotal role in creating an environment conducive to academic and project excellence. Special thanks to \textbf{Ms. Anjali Pandey} for her continuous support as well, contributing to the dynamic learning atmosphere.}

\large{\paragraph{}
I would also like to express my appreciation to my peers and colleagues who actively participated in discussions, shared innovative ideas, and collaborated on various aspects of the project development. The collective effort and camaraderie among us have contributed to a holistic learning and development experience.}

\large{\paragraph{}
Lastly, I extend my sincere thanks to my family and friends for their steadfast encouragement and understanding during the demanding phases of this B.Tech project. Their unwavering support has been a constant source of motivation.}

\large{\paragraph{}
In conclusion, I acknowledge the collective efforts of all those who have played a role, directly or indirectly, in the successful completion of this project. Your contributions are deeply appreciated and have been instrumental in shaping this development journey.}

\begin{flushright}
{
\vspace{1cm}
\textbf{VIVEK SHEKHAWAT}\\
\textbf{21ESKIT122}\\
\vspace{.5cm}
}
\end{flushright}
\newpage
