\chapter{NON-FUNCTIONAL REQUIREMENTS}

\raggedright

\section{Security}
\large{\paragraph{}
The Quiz App prioritizes the security of user data and maintains a secure user experience. Implementation includes measures to protect user information and ensure data integrity. Securing the connection to external services, such as the APIs used for student and faculty interactions, is achieved through secure authentication methods and encryption. Regular security audits and penetration testing are conducted to identify and mitigate vulnerabilities.}

\section{Scalability}
\large{\paragraph{}
The Quiz App is designed to handle increasing user loads, data growth, and traffic demands without compromising performance or user experience. Scalability is a crucial aspect to provide a seamless and reliable experience to users as the platform expands in size and popularity. The system architecture is optimized to scale horizontally, ensuring efficient resource utilization and load distribution.}

\section{Maintainability}
\large{\paragraph{}
To enhance maintainability, the Quiz App codebase is structured into modular components, adhering to best practices for code organization and separation of concerns. Comprehensive and up-to-date documentation is provided to assist developers in understanding and maintaining the codebase. Regular code reviews are conducted to maintain code quality and share knowledge among the development team.}

\section{Localization}
\large{\paragraph{}
The Quiz App is designed to be accessible to a diverse global audience. It implements mechanisms for translating user-generated content and quiz questions into different languages. The system detects users' preferred languages and adjusts the content and user interface accordingly. Date, time, and currency values are displayed in alignment with the user's locale to provide a personalized experience.}

\section{Performance}
\large{\paragraph{}
The Quiz App is optimized for efficient performance, ensuring quick response times for user interactions. Server response times are monitored and maintained within acceptable limits. Performance testing is conducted under varying user loads to identify and address any bottlenecks or performance issues.}

\section{Reliability}
\large{\paragraph{}
The Quiz App aims for high reliability, minimizing downtime and ensuring uninterrupted access to quizzes and user data. The system is designed with fault tolerance, and regular backups are performed to safeguard against data loss. A robust error-handling mechanism is implemented to gracefully handle unexpected issues and provide a reliable user experience.}

\section{Usability}
\large{\paragraph{}
Usability is a key focus for the Quiz App, ensuring an intuitive and user-friendly interface. User feedback is regularly collected and used to improve the user experience. The application is designed to be accessible to users with diverse technical backgrounds, and user interface elements are organized logically to facilitate easy navigation.}

\section{Accessibility}
\large{\paragraph{}
The Quiz App adheres to accessibility standards, making it usable by individuals with disabilities. The application supports screen readers, keyboard navigation, and other assistive technologies. Text and multimedia content are designed to be perceivable, operable, and understandable by a wide range of users.}

\section{Availability}
\large{\paragraph{}
The Quiz App is designed to be available 24/7, ensuring continuous access for users. Regular maintenance activities, updates, and deployments are scheduled during low-traffic periods to minimize disruptions. The system includes redundancy and failover mechanisms to mitigate the impact of potential server failures.}
